---
title: "project1"
author: "Liwei Zhang"
date: "January 31, 2019"
output: html_document
---


```{r echo=FALSE, results='hide',message=FALSE}
library(tidytext)
library(dplyr)
library(stringr)
library(magrittr)
library(ggplot2)
library(tidyr)
library(scales)
library(topicmodels)
library(tm)
library(wordcloud)
library(wordcloud2)
library(RColorBrewer)
library(data.table)
```

```{r echo=FALSE, results='hide',message=FALSE}
#hm_data<-read.csv("/Users/liweizhang/Columbia University/cu_semester2/Applied Data Science/project1/project/processed_moments2.csv")

hm_data<-read.csv("C:/Users/lz2655/Downloads/processed_moments_new.csv")
#create age groups
hm_data<-hm_data[!is.na(hm_data$age),]
hm_data$revised_age<-as.numeric(hm_data$age)
hm_data$revised_age<-ifelse(hm_data$revised_age=="prefer not to say",mean(hm_data$revised_age),hm_data$revised_age)

age_breaks<-c(0,20,30,40,50,150)
age_labels<-c("<20","20-30","30-40","40-50",">50")
setDT(hm_data)[ , agegroups := cut(revised_age, 
                                breaks = age_breaks, 
                                right = FALSE, 
                                labels = age_labels)]
```

```{r echo=FALSE, results='hide',message=FALSE}
num_female<-nrow(subset(hm_data,gender=="f"))
num_male<-nrow(subset(hm_data,gender=="m"))

num_married<-nrow(subset(hm_data,marital=="married"))
num_single<-nrow(subset(hm_data,marital=="single"))
```


```{r echo=FALSE, results='hide',message=FALSE,warning=FALSE}
#tokenize the sentences
order_wid<-order(hm_data$wid)#order hm_data by wid
hm_data<-hm_data[order_wid,]

df<-data_frame(wid=hm_data$wid,gender=hm_data$gender,marital=hm_data$marital,text=as.character(hm_data$text))
df<-df %>%
 unnest_tokens(word,text)
```

##Sentiment analysis

###Things to cheer people up 
To see generally what happens usually at people's happy monents, I use NRC Lexicons to find the most frequent sentiment words.
```{r echo=FALSE, results='hide',message=FALSE}
#show most common words
sentiments_nrc<-get_sentiments("nrc")

df_nrc<-df %>% 
  inner_join(sentiments_nrc) %>%
  count(word, sort = TRUE)

data_tmp <-data.frame(df_nrc[1:10,])
data_tmp$word<-as.vector(data_tmp$word)
data_tmp$word<-factor(data_tmp$word,data_tmp$word)
ggplot(data_tmp)+
  geom_bar(stat="identity",aes(x=word,y=n,col="#F8766D"),fill="#F8766D")+
 # coord_flip()+
  labs(title = "Top 10 frequent sentiment words",y="Number",x="Words")+
  theme(legend.position = 'none')+
  theme_bw()+
  theme(
    plot.background = element_blank()
    ,panel.grid.major = element_blank()
    ,panel.border = element_blank())
#library(scales)
# show_col(hue_pal()(4))
# hue_pal()(4)
#[1] "#F8766D" "#7CAE00" "#00BFC4" "#C77CFF"
```

```{r echo=FALSE, results='hide',message=FALSE}
#get joy with nrc
nrc_joy<-get_sentiments("nrc") %>%
  filter(sentiment=="joy")
df_joy<-df %>% 
  inner_join(nrc_joy) 
df_joy

#get "joy" sentiment percent within males, females, married people and single ones
p_joy_male<-nrow(df_joy[df_joy$gender=="m",])/num_male
p_joy_female<-nrow(df_joy[df_joy$gender=="f",])/num_female

p_joy_married<-nrow(df_joy[df_joy$marital=="married",])/num_married
p_joy_single<-nrow(df_joy[df_joy$marital=="single",])/num_single
```

```{r echo=FALSE, results='hide',message=FALSE}
#r get trust with nrc
nrc_trust<-get_sentiments("nrc") %>%
  filter(sentiment=="trust")
df_trust<-df %>% 
  inner_join(nrc_trust)
df_trust

#get "trust" sentiment percent within males, females, married people and single ones
p_trust_male<-nrow(df_trust[df_trust$gender=="m",])/num_male
p_trust_female<-nrow(df_trust[df_trust$gender=="f",])/num_female

p_trust_married<-nrow(df_trust[df_trust$marital=="married",])/num_married
p_trust_single<-nrow(df_trust[df_trust$marital=="single",])/num_single
```


```{r echo=FALSE,results="hide", message=FALSE}
#get surprise with nrc
nrc_surprise<-get_sentiments("nrc") %>%
  filter(sentiment=="surprise")
df_surprise<-df %>% 
  inner_join(nrc_surprise)
df_surprise

#get "surprise" sentiment percent within males, females, married people and single ones
p_surprise_male<-nrow(df_surprise[df_surprise$gender=="m",])/num_male
p_surprise_female<-nrow(df_surprise[df_surprise$gender=="f",])/num_female

p_surprise_married<-nrow(df_surprise[df_surprise$marital=="married",])/num_married
p_surprise_single<-nrow(df_surprise[df_surprise$marital=="single",])/num_single
```
###Sentiment comparison within groups
I want to find whether there is a difference of sentiment expressions between female and male groups or married and single groups. To examine it, I first divide the data into female and male as well as married and single, respectively. After that, I compute the frequency of the use of sentiment words and scale the frequency by the total sentence number of each group. Here are two plots below that show the scaled frequency for each group.

```{r echo=FALSE,message=FALSE}
#r compare the three sentiment within male and female
x_gender<-c("joy","trust","surprise","joy","trust","surprise","f","f","f","m","m","m",p_joy_female,p_trust_female,p_surprise_female,p_joy_male,p_trust_male,p_surprise_male)

gender_sentiments<-data.frame(matrix(x_gender,nrow = 6,ncol = 3))
colnames(gender_sentiments)<-c("sentiments","gender","scaled_frequency")#create new dataframs to plot

ggplot(gender_sentiments,aes(sentiments,scaled_frequency,fill=gender))+
  geom_bar(stat="identity",position="dodge")+
  theme_bw()+
  labs(title="Useage of sentiment words over gender", y="scaled frequency")+
  theme(
    plot.background = element_blank()
    ,panel.grid.major = element_blank()
    ,panel.border = element_blank())
```

```{r echo=FALSE,message=FALSE}
#compare the three sentiment within married people and single ones
x_marital<-c("joy","trust","surprise","joy","trust","surprise","married","married","married","single","single","single",p_joy_married,p_trust_married,p_surprise_married,p_joy_single,p_trust_single,p_surprise_single)

marital_sentiments<-data.frame(matrix(x_marital,nrow = 6,ncol = 3))
colnames(marital_sentiments)<-c("sentiments","marital","scaled_frequency")#create new dataframs to plot

ggplot(marital_sentiments,aes(sentiments,scaled_frequency,fill=marital))+
  geom_bar(stat="identity",position="dodge")+
  theme_bw()+
  labs(title="Useage of sentiment words over marital", y="scaled frequency")+
  theme(
    plot.background = element_blank()
    ,panel.grid.major = element_blank()
    ,panel.border = element_blank())
```
 
* Compared to male group, female group shows stronger sentiments by having higher scaled frequency of using sentiment words. 

* Compared to single group, married group shows stronger sentiments by having higher scaled frequency of using sentiment words. 

* For all groups, they enjoyed the moment of joy the most, then that of trust and then that of surprise.


##tf-idf
```{r echo=FALSE,results="hide",message=FALSE}
#get the word frequency by gender
df_word_gender<-df %>% 
  count(gender,word,sort = TRUE)

tmp<-df_word_gender%>%
  group_by(gender)%>%
  summarize(total=sum(n))

df_word_gender<-left_join(df_word_gender,tmp)

freq_by_rank_gender<-df_word_gender%>%
  group_by(gender)%>%
  mutate(rank=row_number(),'term frequency'=n/total)

df_word_gender<-df_word_gender%>%
  bind_tf_idf(word,gender,n)

df_word_gender
```



```{r echo=FALSE,results="hide",message=FALSE}
df_word_gender<-df_word_gender%>%
  select(-total)%>%
  arrange(desc(tf_idf))

df_word_gender
```

```{r echo=FALSE, message=FALSE}
df_word_gender%>%
  arrange(word=factor(word,levels=rev(unique(word))))%>%
  group_by(gender)%>%
  top_n(15)%>%
  ungroup()%>%
  ggplot(aes(word,tf_idf,fill=gender))+
  geom_col(show.legend = FALSE)+
  labs(title="tf_idf by gender",x=NULL,y="tf_idf")+
  facet_wrap(~gender,ncol=2,scales = "free")+
  coord_flip()
```




```{r echo=FALSE,results="hide",message=FALSE}
#get the word frequency by marital situation
df_word_marital<-df %>% 
  count(marital,word,sort = TRUE)

tmp<-df_word_marital%>%
  group_by(marital)%>%
  summarize(total=sum(n))

df_word_marital<-left_join(df_word_marital,tmp)

freq_by_rank_marital<-df_word_marital%>%
  group_by(marital)%>%
  mutate(rank=row_number(),'term frequency'=n/total)

df_word_marital<-df_word_marital%>%
  bind_tf_idf(word,marital,n)

df_word_marital<-df_word_marital%>%
  select(-total)%>%
  arrange(desc(tf_idf))

df_word_marital
```

```{r echo=FALSE, message=FALSE}
df_word_marital%>%
  arrange(word=factor(word,levels=rev(unique(word))))%>%
  group_by(marital)%>%
  top_n(15)%>%
  ungroup()%>%
  ggplot(aes(word,tf_idf,fill=marital))+
  geom_col(show.legend = FALSE)+
  labs(title="tf_idf by marital",x=NULL,y="tf_idf")+
  facet_wrap(~marital,ncol=2,scales = "free")+
  coord_flip()
```
Under tf-idf method, what married people enjoy is as followed.

* Family trips 
There are six top words about tourist attractions and amusement parks. They include Wonderla(amusement park), Wayanad, Tioman, Ariyaman(tourist attractions), Munnar,Thekkady(national park),etc)

* Family life
There are words such as grandkids and father-in-law.

* Real estate purchases
ex. bhk(one bedroom, one hall and one kitchen apartment)


Under tf-idf method, what single people enjoy is as followed.
* Single life(Tinder, Coachella )
* Fraternities and sororities(fraternities and Manga)
* Nature(mth=>warth, rain dew)
* Work(fininsh online module)
* Exercise and weightlift(deadlift)
* food (boba)


* Married ones focus more on enjoying family time and settleing down in life.
* Single ones focus more on personal life in both self-entertainment and personal development. 





#gender
```{r,echo=FALSE, message=FALSE,warning = FALSE}
set.seed(0)
demoFreq_f<-data.frame(words = df_word_gender[df_word_gender$gender=="f",]$word, freq =df_word_gender[df_word_gender$gender=="f",]$tf_idf)
wordcloud2(demoFreq_f)
```

```{r,echo=FALSE, message=FALSE,warning = FALSE}
set.seed(0)
demoFreq_m<-data.frame(words = df_word_gender[df_word_gender$gender=="m",]$word, freq =df_word_gender[df_word_gender$gender=="m",]$tf_idf)
wordcloud2(demoFreq_m)
```

```{r,echo=FALSE, message=FALSE,warning = FALSE}
# wordcloud by marital
demoFreq_s<-data.frame(words = df_word_marital[df_word_marital$marital=="single",]$word, freq =df_word_marital[df_word_marital$marital=="single",]$tf_idf)
wordcloud2(demoFreq_s)
```



```{r,echo=FALSE, message=FALSE,warning = FALSE}
demoFreq_ma<-data.frame(words = df_word_marital[df_word_marital$marital=="married",]$word, freq =df_word_marital[df_word_marital$marital=="married",]$tf_idf)
wordcloud2(demoFreq_ma)
```

```{r,echo=FALSE, message=FALSE,warning = FALSE}
wordcloud(words = df_word_marital[df_word_marital$marital=="single",]$word, freq =df_word_marital[df_word_marital$marital=="single",]$tf_idf, min.freq = 1,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))

wordcloud(words = df_word_marital[df_word_marital$marital=="married",]$word, freq =df_word_marital[df_word_marital$marital=="married",]$tf_idf, min.freq = 1,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))
```

#LDA
```{r}
#df_new<-data_frame(category=hm_data$predicted_category,marital=h_text=as.character(hm_data$text))
#df_tm<-df_new %>%
# unnest_tokens(word,text)
#df_tm

```

```{r}
#manual_stopword<-c("day","time")

#df_tm <- df_tm %>% 
#  filter(!(word %in% manual_stopword))
#head(df_tm) 

#df_tm<-df_tm %>% 
#  count(category,word,sort = TRUE)

#df_tm<-df_tm%>%
#   cast_dtm(category,word,n)
#df_tm


#df_lda<-LDA(df_tm,k=15,control = list(seed=0))
#df_lda
```



```{r}
#df_topics<-tidy(df_lda,matrix= "beta")
#df_topics

#top_terms<-df_topics%>%
#  group_by(topic)%>%
#  top_n(5,beta)%>%
#  ungroup()%>%
#  arrange(topic,-beta)
#top_terms
```








```{r}
#df_2<-data_frame(wid=hm_data$wid,gender=hm_data$gender,marital=hm_data$marital,age=hm_data$agegroups,text=as.character(hm_data$text))
#df_2<-df_2 %>%
 #unnest_tokens(word,text)
#df_2
```



```{r}
#df_topics<-tidy(df_lda,matrix("beta"))
#df_topics

#top_terms<-df_topics%>%
#  group_by(topic)%>%
 # top_n(5,beta)%>%
 # ungroup()%>%
 # arrange(topic,-beta)
#top_terms
```



```{r}
#top_terms%>%
#  mutate(term=reorder(term,beta))%>%
 # ggplot(aes(term,beta,fill=factor(topic)))+
#  geom_col(show.legend = FALSE)+
#  facet_wrap(~topic, scales="free")+
#  coord_flip()
```


```{r}
#df_tm<-data.frame(df_2)
#gender_marital_age<-paste(as.character(df_tm$gender),as.character(df_tm$marital),as.character(df_tm$age),sep=".")
#df_tm <-data.frame(cbind(df_tm,gender_marital_age))
#head(df_tm)
```


```{r LDA by gender}
#manual_stopword<-c("friend","day","time","family")

#df_tm <- df_tm %>% 
#  filter(!(word %in% manual_stopword))
#head(df_tm) 

#df_tm<-df_tm %>% 
#  count(gender_marital_age,word,sort = TRUE)

#df_tm<-df_tm%>%
#   cast_dtm(gender_marital_age,word,n)
#df_tm

##df_lda<-LDA(df_tm,k=10,control = list(seed=0))
```


```{r}
#df_topics<-tidy(df_lda,matrix("beta"))
#df_topics

#top_terms<-df_topics%>%
#  group_by(topic)%>%
#  top_n(5,beta)%>%
#  ungroup()%>%
#  arrange(topic,-beta)
#top_terms
```


```{r}
#top_terms%>%
#  mutate(term=reorder(term,beta))%>%
#  ggplot(aes(term,beta,fill=factor(topic)))+
#  geom_col(show.legend = FALSE)+
#  facet_wrap(~topic, scales="free")+
#  coord_flip()
```


```{r}
#n_topics <-c(2, 4, 10, 20, 50, 100)
#ap_lda_compare <- n_topics %>%
#  map(LDA, x = df_word_marital, control =list(seed = 1109))

#geom_point() +
#  y = "Perplexity")

```











